Solution-aware vs global ReLU selection: \\ partial MILP strikes back for DNN verification

### 2025-01-31 CAV 2025 TODO/introduction.tex
update

	\item On the first question, we adapted from BaB-SR \cite{BaB} and FSB \cite{FSB}, which choose branching nodes for BaB, global scoring (GS) functions to choose ReLU for pMILP. 
	These revealed to be much more accurate than the simple heuristic in 
	\cite{DivideAndSlide}. We uncover however one case (out of 4) where the exact function that GS tries to approximate depends heavily upon the mode of the ReLU function, giving very different result for each mode. This implies that these strategies may not be that accurate, because they do not know the mode to choose from. We then designed a novel solution-aware scoring (SAS), which uses the solution of a unique LP call, that provides the mode to consider. Theoretically, we show that SAS is always an over-approximation of the real improvement (Proposition \ref{prop2}), which implies that a small SAS value implies that the ReLU is unnecessary. Experimentally, we further show that SAS is very close to the actual improvement, closer than GS, and that overall, the accuracy from SAS is significantly better than GS.  Compared with the heuristic in \cite{DivideAndSlide}, SAS is much more efficient ($\approx 4$ times less integer variables for same accuracy (Table \ref{tab:example1})).We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally.

>>>>

	\item On the first question, we adapted from BaB-SR \cite{BaB} and FSB \cite{FSB}, which choose branching nodes for BaB, global scoring (GS) functions to choose ReLU for pMILP. 
	These revealed to be much more accurate than the simple heuristic in 
	\cite{DivideAndSlide}. We uncover however one case (out of 4) where the exact function that GS tries to approximate depends heavily upon the mode of the ReLU function, giving very different result for each mode. This implies that these strategies may not be that accurate, because they do not know the mode to choose from. We then designed a novel solution-aware scoring (SAS), which uses the solution of a unique LP call, that provides the mode to consider. Theoretically, we show that SAS is always an over-approximation of the real improvement (Proposition \ref{prop2}), which implies that a small SAS value implies that the ReLU is unnecessary. Experimentally, we further show that SAS is very close to the actual improvement, closer than GS, and that overall, the accuracy from SAS is significantly better than GS.  Compared with the heuristic in \cite{DivideAndSlide},  SAS is much more efficient ($\approx 4$ times less integer variables for same accuracy (Plot \ref{fig_table3})).We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally.
